---
title: "Customizing forms -- NF example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{customizing-forms-NF-example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Intro

This vignette provides a walk-through of actual usage for the NF project, focusing on the DSP form. 
To provide some context, NF groups projects under 4 different funding mechanisms/agencies (though there can be overlap or co-funding for projects), which are:  

- NTAP  
- CTF  
- GFF  
- DHART-SPORE  

Hence, there needs to be four versions of the forms. 
We show the setup and adaptation of the base form to varying degrees for each version.

See also related vignettes (TO DO):

- More complicated customizations
- Retrieve JSON data and generate PDF

## Organization

First, we organize things by creating a directory for each of the funders ([see on GitHub](https://github.com/nf-osi/forms)).

Then, in CTF for example, we set up version 1 of the DSP with:

`formd::draftStandardDSP(version = "v1")`

This creates a folder called DSP_Standard_v1 ([see on GitHub](https://github.com/nf-osi/forms/tree/main/CTF)).

In this manner, future newer versions of the same form, or other form types are located in their own form folders.

## Adaptation

As mentioned, forms can be adapted to varying degrees. 
The more your use case departs from NF, the more you will have to think about this process. 
For NF, the different levels of tweaking are summarized in the table below. 
Note that NTAP and CTF were the original templates, so there were no real customizations for these.

Column description:  

- **Funder**: Label of funder version.
- **Doc**: The original Word/Google docs version
- **Commit**: Actual commit showing how parameters/files are customized in Rmarkdown; use as comparisons/examples of what might be expected.
- **Degree**: Relative degree of customization; this is also obvious by looking at param/file changes in the linked commit.
- **Html**: Live version of HTML form when rendered (after the custom commit / suggestion to compare with doc version)

```{r setup, echo=FALSE}
library(formd)
```

```{r summary, echo=FALSE}
example_summary <- data.frame(
  Funder = c("CTF", "NTAP", "DHART-SPORE", "GFF"),
  Doc = c("https://docs.google.com/document/d/1fhtjpvq1r4-QqB9YjG5KICW4pPDtRQpKkdlhPN1xMbk", "https://docs.google.com/document/d/1aa7061ekrk5qbFVnB7pRahnN1hDd0Ut_090QzdP0UyU", "https://docs.google.com/document/d/1JC8eNOS2bnrpIJhEX3zqLmqYTHUDF7Ui7xe139kBcCU", "https://docs.google.com/document/d/1ib4RreL_UL7AC7NKgKFIu_8PBvJDeQxfNN7qDHh4GfI"),
  Commit = c("https://github.com/nf-osi/forms/commit/9ebe5d260a5d0e3e06c5702d99e0edcba5acd170", "https://github.com/nf-osi/forms/commit/25cae2d8785e6d23103db40d4d55776bda92a9e1", "https://github.com/nf-osi/forms/commit/96d6089ad83f95c55c9d1f997c0870ab96e6bf30", "https://github.com/nf-osi/forms/commit/47735004847ff90d599d3f4322370c890b601059"),
  Degree = c("basic params", "basic params", "basic params + wording", "basic params + new inputs + wording"),
  Html = c("https://nf-osi.github.io/forms/CTF/DSP_Standard_v1/DSP_Standard_v1.html", "https://nf-osi.github.io/forms/NTAP/DSP_Standard_v1/DSP_Standard_v1.html", "https://nf-osi.github.io/forms/DHART-SPORE/DSP_Standard_v1/DSP_Standard_v1.html", "https://nf-osi.github.io/forms/GFF/DSP_Standard_v1/DSP_Standard_v1.html")
)
knitr::kable(example_summary) 
```



